---
title: "Network Analysis"
---
The organisation has providede the csv. file of Email headers information. It is obvious that the network relationship from email header data should be drawed as direct graph. 

The code chunks below are used to explore the connections for those email users.

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(fig.retina = 3,
                      echo = TRUE, 
                      eval = TRUE,
                      error = FALSE, 
                      message=FALSE, 
                      warning=FALSE)
```

```{r}
packages = c('tidytext','widyr','visNetwork','DT','dplyr','textplot','lubridate','tidyverse','tidygraph','ggraph','igraph','stringr','clock')
for (p in packages){
  if (!require(p,character.only = T)){
    install.packages(p)
  }
  library(p,character.only = T)
}
```

```{r}
email <- read_csv("data/emailheader.csv")
```


```{r}
library(tidyr)
raw <- separate(email, col = From, into = c("from", "suffix"), sep = "@")
```

```{r}
view_data <- raw %>%
  group_by(from) %>%
  summarize(number_rows = n())
```

```{r}
view_data <- raw %>%
  select(-c(suffix))%>%
  separate_rows(To, sep = ", ") 
```

```{r data preparation}
email1 <- separate(view_data, col = To, into = c("to", "suff"), sep = "@") %>%
  select(-c(suff))%>%
  filter(from!=to)%>%
  arrange(from) 
```

```{r}
g <- graph_from_data_frame(email1, directed = TRUE) 
```

```{r}
is.directed(g)
```
```{r}
is.weighted(g)
```
```{r}
table(head_of(g,E(g)))
```
**Make a basic plot**
```{r}
plot(g, 
     vertex.label.color = "black", 
     edge.color = 'gray77',
     vertex.size = 1,
     edge.arrow.size = 0.3,
     layout = layout_nicely(g))
```

**Is there an edge going from vertex Adan.Morlun to vertex Benito.Hawelon?**
```{r}
g['Adan.Morlun', 'Benito.Hawelon']
```
**Show all edges going to or from vertex Adan.Morlun**
```{r}
incident(g, 'Adan.Morlun', mode = c("all"))
```
**Show all edges going out from vertex Adan.Morlun**
```{r}
incident(g, 'Adan.Morlun', mode = c("out"))
```

**Calculate the out-degree of each vertex**
```{r}
g.outd <- degree(g, mode = c("out"))
```

**View a summary of out-degree**
```{r}
table(g.outd)
```

**Make a histogram of out-degrees**
```{r}
hist(g.outd, breaks = 30)
```

**Find the vertex that has the maximum out-degree**
```{r}
which.max(g.outd)
```

**Calculate betweenness of each vertex**
```{r}
g.b <- betweenness(g, directed = TRUE)
```

**Show histogram of vertex betweenness**
```{r}
hist(g.b, breaks = 80)
```

**Make an ego graph**
```{r}
gAM <- make_ego_graph(g, diameter(g), nodes = 'Adan.Morlun', mode = c("all"))[[1]]
```

**Get a vector of geodesic distances of all vertices from vertex Adan.Morlun**
```{r}
dists <- distances(gAM, "Adan.Morlun")
```

**Create a color palette of length equal to the maximal geodesic distance plus one.**
```{r}
colors <- c("black", "red", "orange", "blue", "dodgerblue", "cyan")
```

**Set color attribute to vertices of network gAM.**
```{r}
V(gAM)$color <- colors[dists+1]
```


**Visualize the network based on geodesic distance from vertex Adan.Morlun (patient zero).**

```{r}
plot(gAM, 
     vertex.label = dists, 
     vertex.label.color = "white",
     vertex.label.cex = .006,
     edge.color = 'darkgreen',
     vertex.size = 1,
     edge.arrow.size = .05,
     main = "Geodesic Distances from Patient Zero")
```
**Inspect Forrest Gump Movie dataset**
```{r}
head(email1)
```

```{r}
g2 <- graph_from_data_frame(email1, directed = TRUE)
```

**Identify key nodes using eigenvector centrality**
```{r}
g.ec <- eigen_centrality(g2)
which.max(g.ec$vector)
```

**Plot Forrest Gump Network**
```{r}
plot(g2,
vertex.label.color = "black", 
vertex.label.cex = 0.6,
vertex.size = 25*(g.ec$vector),
edge.color = 'gray88',
main = "GASTech Email Network"
)
```

